%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%\colorlet{awesome}{awesome-red}
% Uncomment if you would like to specify your own color
\definecolor{awesome}{HTML}{006ec7}

% colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
% \photo[circle,noedge,left]{./examples/profile}
\name{Jonas}{Falck}
\position{Web-Development - Data-Analysis - Bioinformatics}
\address{Holzstraße 1, 44869, Bochum, Germany}

\mobile{(+31) 655707314}
\email{jonas@falcken.de}
\homepage{joe-nas.github.io}
\github{joe-nas}
%\linkedin{posquit0}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra informations}

% \quote{``rtfm"}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Human Resources Department}
  {adesso}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Application: Software Developer Java @ adesso}
% How the letter is opened
\letteropening{Dear Hiring Team,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
%\letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Jonas Falck~~~·~~~Motivation}
  {}

% Print the title with above letter informations
\makelettertitle
%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

\lettersection{About Me}
After completing my civil service duty, I moved from Bochum to the Netherlands to study medical biology in Nijmegen. 
I completed my bachelor’s degree and began my master's in medical epigenomics at the Radboud University. 
During this time, both in- and outside of university, I focused on developing IT skills such as setting up and managing headless Linux systems, programming with a focus on bioinformatics, machine learning and web-development. 
I honed my data-analysis skills during my master's internships in the Radboud UMC human genetics department, as well as in the comparative genomics group. 
Due to financial and personal reasons, I got stuck in a logistics job for many years and did not finish my masters.
A year, ago I quit my logistics job to focus on extending my tech skills and to find a job which aligns with my passion for IT as well my education.
Apart from my professional goals, I enjoy going to concerts, bouldering, learning new skills and most importantly, spending time with my friends and family.
\lettersection{Why Software Development @ adesso}
I am eager to work as a software developer at adesso, because adesso is one of the top IT service providers in Germany, to implement individualized software solutions and to drive digitalization forward.
Adesso has a wide range of prominent clients from various industries, and I am confident that you have a lot of interesting and challenging projects to work on and to learn from.
Moreover, I am excited that adesso offers the opportunity to be involved in the entire software development cycle as well as project management process, enabling growth and skill development in a hands-on fashion.
After reviewing the adesso learning guide, I am convinced that adesso is the right place for me to grow and develop my skills.
Besides growing on a professional level, I am looking for a company which is known for a positive work environment, where employees work in a team-oriented, supportive, and respectful manner.
Given adesso has consecutively been awarded as a top employer in Germany, I am confident that it is the right place for me to grow and develop my skills.
\lettersection{Why Me?}
While my career path may not have been straightforward, my journey as a career changer has equipped me with diverse experiences and a unique perspective, making me an ideal candidate for this position.
I am not just excited about working as a software developer, but I am also tech-savvy with hands-on experience in web-development, data analysis, integration of large amounts of heterogeneous data as well as documenting and testing my work.
During my academic journey, I developed a passion for working with large amount of biological data, its analysis, machine learning and the associated technical and computational aspects.
As I am intrinsically motivated to learn, I dedicated considerable time to discover, learn and develop the tools essential to achieve my goals.
I am proficient in R for statistical programming and data visualization, Python for data analysis, machine learning as well as Bash for automating tasks and managing Linux systems.
In terms of web development, I have focused on utilizing Java and JavaScript, leveraging frameworks like Spring, React, and Next.js. 
I prefer a hands-on approach to learning, evident in projects such as developing a workout tracker using Java and JavaScript and creating an R package to streamline data analysis of millions of data points during my master internships.
Furthermore, I am confident in my ability to develop solutions for given problems, troubleshoot complex issues as well as the ability to pick up and learn technology as I go.
While I value being able to work independently, I appreciate having knowledgeable peers around to discuss stubborn problems and to learn and grow from.
As a hands-on and down-to-earth person, as well as a hard worker, I would be pleased to meet with you soon.
\end{cvletter}
%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing
\end{document}
